## Q-Q Plot

In the last section, we learned how to use cdf and ccdf plots to detect if observed data follow a well-known probability distribution such as the exponential or the normal distribution. An alternative visual tool for that purpose is the Q-Q plot. Let's start with an example. Let's generate 500 data points from a standard normal distribution and draw a Normal Q-Q plot (also called Normal Probability Plot) of the sampled data.

```{r, qqplot_smp_p1, fig.cap="Q-Q plot of standard normal sample data with point-wise confidence band"}
library(ezplot)
library(dplyr)
set.seed(0)
smp = data.frame(x = rnorm(500))
plt = mk_qqplot(smp)
plt("x", dist = 'norm')
```

We see almost all data points are along the 45 degree diagonal line and within 
the point-wise confidence band. This tells us the data are normally 
distributed. (What else can it be? The data are randomly drawn from a standard 
normal distribution.) Alternatively, we can draw the Aldor-Noiman tail-sensitive confidence band by setting `ci_band_type = "ts"`.

```{r, qqplot_smp_p2, fig.cap="Q-Q plot of standard normal sample data with tail-sensitive confidence band"}
plt("x", ci_band_type = "ts")
```

Not only qqplot can be used to check normality, it can also be used to check if
observed data follow these distributions: beta, cauchy, chi-squared, exponential, F, gamma, geometric, log-normal, logistic, binomial, poisson, t, and weibull. For example, let's check if the ozone levels from the air quality data are exponentially distributed.

```{r, qqplot_ozone, fig.cap="Exponential Q-Q Plot of Ozone Levels"}
plt = mk_qqplot(airquality)
plt("Ozone", dist = "exp", dparams = list(rate = 0.022)) %>% 
        add_labs(title = "Ozone levels are more or less exponential",
                 caption = "Model: Exponential(rate = 0.022)")
```

In the code block above, we set `dist = "exp", dparams = list(rate = 0.022)`. 
This tells `plt()` to compare the empirical distribution of the observed ozone levels with an exponential distribution of rate 0.022. 

Now it's your turn. Try the following exercises.

1. Read the document of `mk_qqplot()` and run the examples. You can pull up the 
document by running `?mk_qqplot` in Rstudio. 
2. Draw a qqplot to check if the `boxoffice` variable from the `films` data is normally distributed. What about `boxoffice` of action films that made money? Are they normally distributed? What about their log-transformed values? (If the log-transformed values are normally distributed, the original values are called log-normal.)
