## Bar Chart

A bar chart is often used for displaying the distribution (a.k.a., the frequencies or percentages of the levels) of a categorical variable. When making a bar chart, the first step is to count the frequencies and/or calculate the corresponding percentages of all the levels in that categorical variable. For example, the `mpaa` variable in the data frame `films` has 4 levels: NC-17, PG, PG-13 and R, and we can tally up their frequencies and percentages using the following code.
```{r}
library(ezplot)
tbl = table(films$mpaa)
tbl_cnt = data.frame(tbl)
names(tbl_cnt) = c("lvl", "cnt")
tbl_pct = data.frame(prop.table(tbl))
names(tbl_pct) = c("lvl", "pct")
tbl = merge(tbl_cnt, tbl_pct)
tbl
```      
  
We can then draw bar charts to display them, but first, let's get some color-blind friendly colors.
```{r}
purple = cb_color("reddish_purple")
green = cb_color("bluish_green")
red = cb_color("vermilion")
blue = cb_color("blue")
```

Now let's draw bar charts using these color-blind friendly colors.
```{r, barplot_mpaa_cnt, fig.cap="Distribution of MPAA - Frequency"} 
plt = mk_barplot(tbl)
title = "Frequency of Each MPAA Rating"
p = plt("lvl", "cnt", fillby="lvl", main=title, legend=F)
p = scale_axis(p, scale="comma")  
p = p + ggplot2::scale_fill_manual(values = c(purple, green, red, blue))
p
```  
  
```{r, barplot_mpaa_pct, fig.cap="Distribution of MPAA - Percentage"} 
title = "Percentage of Each MPAA Rating"
p = plt("lvl", "pct", fillby="lvl", main=title, legend=F)
p = scale_axis(p, scale="pct", pct_jump=0.25)
p = p + ggplot2::scale_fill_manual(values = c(purple, green, red, blue))
p
```

Sometimes, we may want to label the bars with the frequencies or percentages. To do that, we need to first use the function `add_bar_label_pos()` to prep data a little bit. 
```{r}
# make a function that can be used to append columns of 
# bar label positions to the input data frame
f = add_bar_label_pos(tbl)
# append bar label positions based on pct
tbl = f("lvl", "pct", vpos=0.03) # if putting labels at the top of the bars, label positions are 0.03 higher than values of pct.
tbl
```

We see `tbl` has two extra columns now, namely, `pct_pos_top` and `pct_pos_mid`. The former is the label position if we choose to put the labels above the bars, and the latter is the label position if we choose to put the labels in the middle of the bars. We can use these two columns when the y-axis is percent, like in the second plot above. We can also append to `tbl` two more columns of label positions based on the variable `cnt`. For example, we can run the following code to append to `tbl` the columns `cnt_pos_top` and `cnt_pos_mid`, which can be used when the y-axis is frequency, like in the first plot shown above. 
```{r}
# because tbl is updated, we need to call add_bar_lable_pos again
f = add_bar_label_pos(tbl)
# append bar label positions based on cnt
tbl = f("lvl", "cnt") # if putting labels at the top of the bars, label positions are 0.2 higher than values of cnt.
tbl
```

Let's re-draw the above bar charts with labels at the top of the bars.
```{r, barplot_mpaa_cnt_lab_at_top, fig.cap="Distribution of MPAA - Frequency"} 
plt = mk_barplot(tbl)
title = "Frequency of Each MPAA Rating"
p = plt("lvl", "cnt", fillby="lvl", main=title, legend=F,
        barlab="cnt", barlab_at_top=T, barlab_size=5)
p = scale_axis(p, scale="comma")  
p = p + ggplot2::scale_fill_manual(values = c(purple, green, red, blue))
p
```  

```{r, barplot_mpaa_pct_lab_at_top, fig.cap="Distribution of MPAA - Percentage"} 
title = "Percentage of Each MPAA Rating"
p = plt("lvl", "pct", fillby="lvl", main=title, legend=F,
        barlab="pct", barlab_use_pct=T, decimals=2, 
        barlab_at_top=T, barlab_size=5)
p = scale_axis(p, scale="pct", pct_jump=0.25)
p = p + ggplot2::scale_fill_manual(values = c(purple, green, red, blue))
p
```

Let's place the labels in the middle of the bars.
```{r, barplot_mpaa_cnt_lab_in_mid, fig.cap="Distribution of MPAA - Frequency"} 
title = "Frequency of Each MPAA Rating"
p = plt("lvl", "cnt", fillby="lvl", main=title, legend=F,
        barlab="cnt", barlab_at_top=F, barlab_size=5)
p = scale_axis(p, scale="comma")  
p = p + ggplot2::scale_fill_manual(values = c(purple, green, red, blue))
p
```  

```{r, barplot_mpaa_pct_lab_in_mid, fig.cap="Distribution of MPAA - Percentage"}
title = "Percentage of Each MPAA Rating"
p = plt("lvl", "pct", fillby="lvl", main=title, legend=F,
        barlab="pct", barlab_use_pct=T, decimals=2, 
        barlab_at_top=F, barlab_size=5)
p = scale_axis(p, scale="pct", pct_jump=0.25)
p = p + ggplot2::scale_fill_manual(values = c(purple, green, red, blue))
p
```

We can also use bar chart to display the bivariate distribution of two categorical variables. For example, say we want to look at the breakdown of the MPAA ratings for action films vs. non-action films. We can tally the numbers by running ```r with(films, table(action, mpaa))```.

Instead of visualizing all this information, it suffices to only visualize the percent of action films (`action = 1`) for each MPAA rating. The following function allows us to calculate the percent of the 1-level of an arbitrary binary variable for each level of another arbitrary categorical variable.
```{r}
calc_pct_1 = function(dat, xvar, yvar){
        # dat: data frame
        # xvar: string, name of a categorical variable on dat, x-axis 
        # yvar: string, name of a 0-1 binary variable on dat, y-axis
        tbl = table(dat[[yvar]], dat[[xvar]])
        pct = tbl["1", ] / (tbl["0", ] + tbl["1", ])
        pct = data.frame(pct)
        pct = cbind(row.names(pct), pct)
        names(pct) = c(xvar, paste("pct", yvar, "1", sep="_"))
        row.names(pct) = NULL
        pct
}
```

We can use it to calculate the percent of action films for each MPAA rating. Afterwards, we'll visualize these percentages using a bar chart.
```{r, barplot_mpaa_vs_action, fig.cap="Distribution of Action Films Across MPAA Ratings"}
# calculate pct
mpaa_vs_action = calc_pct_1(films, "mpaa", "action")
# append bar label positions based on pct
f = add_bar_label_pos(mpaa_vs_action)
tbl = f("mpaa", "pct_action_1", vpos=0.03)
# make bar chart
plt = mk_barplot(tbl)
title = "Percentage of Action Films for Each MPAA Rating"
p = plt("mpaa", "pct_action_1", fillby="mpaa", main=title, legend=F,
        barlab="pct_action_1", barlab_use_pct=T, decimals=2, 
        barlab_at_top=T, barlab_size=5)
p = scale_axis(p, scale="pct", pct_jump=0.25)
p = p + ggplot2::scale_fill_manual(values = c(purple, green, red, blue))
p
```

Now, it's your turn. Visualize the percentages of dramas across each MPAA rating. Do the same for comedy, romance, thriller and horror films.