### Dodged and Stacked Bar Chart

A dodged or stacked bar chart is often used to show relationships amongst two categorical and one continous variables. For example, take the variables `year_cat` and `made_money` from the data frame `films`. The former brackets time (measured in years) into 4 categories and the latter indicates if a film made money or not. Maybe we are interested in the number or percentage of films made or lost money for each time period. We can use `table()` and `prop.table()` to easily get the answers.
```{r}
library(ezplot)
tbl = with(films, table(year_cat, made_money))
tbl_pct = prop.table(tbl, margin = 1)
print(tbl)
print(tbl_pct)
```      

But of course, instead of reading these numbers, we'd very much want to look at them, so we prefer to turn them into a graph. We'll do that in a moment, but first of all, let's get some colors that are color-blind friendly.
```{r}
purple = cb_color("reddish_purple")
green = cb_color("bluish_green")
red = cb_color("vermilion")
blue = cb_color("blue")
```

And let's turn `tbl` and `tbl_pct` into data frames because ezplot only works with data frames. 
```{r}
dat = data.frame(tbl)
dat_pct = data.frame(tbl_pct)
names(dat) = tolower(names(dat))
names(dat_pct)[3] = "pct"
print(dat)
print(dat_pct)
```
  
Now let's make a dodged bar chart to show the number of films that made or lost money for each time period. 
```{r, barplot_dodged_cnt, fig.cap="Number of Films that Made or Lost Money for Each Time Period"} 
plt = mk_barplot(dat)
title = "Number of Films that Made/Lost Money for Each Time Period"
p = plt("year_cat", "freq", fillby="made_money", barpos="dodge", 
        main=title, ylab = "Count")
p = scale_axis(p, scale="comma")  
p = p + ggplot2::scale_fill_manual(values = c(purple, green))
p
```  
 
To be a little bit fancier, we can label the bars with the actual counts. To do that, we need to first use the function `add_bar_label_pos()` to prep `dat` a little bit. 
```{r}
# split dat into two data frames based on the values of made_money
lst_of_dfs = split(dat, dat$made_money)
dat_no = lst_of_dfs[["no"]]
dat_yes = lst_of_dfs[["yes"]]
# make functions to be used for adding columns of 
# bar label positions to the input data frame
f_no = add_bar_label_pos(dat_no)
f_yes= add_bar_label_pos(dat_yes)
# add bar label positions based on freq
dat_no = f_no("year_cat", "freq", vpos=100) # if putting labels at the top of the bars, label positions are 0.03 higher than values of pct.
dat_yes = f_yes("year_cat", "freq", vpos=100)
# rbind dat_no and dat_yes
dat_w_pos = rbind(dat_no, dat_yes)
print(dat_w_pos)
```

Notice the columns `freq_pos_top` in `dat_w_post`. We'd use it if we want to put the labels above the bars. Let's try it.
```{r, barplot_dodged_cnt_toplab, fig.cap="Number of Films that Made or Lost Money for Each Time Period"} 
plt = mk_barplot(dat_w_pos)
title = "Number of Films that Made/Lost Money for Each Time Period"
p = plt("year_cat", "freq", fillby="made_money", barpos="dodge", 
        main=title, ylab = "Count", 
        barlab="freq", barlab_at_top=T, barlab_size=5)
p = scale_axis(p, scale="comma")  
p = p + ggplot2::scale_fill_manual(values = c(purple, green))
p
```  

At a glance, we see there are more films that made money than not for each period. This is good news. However, the above dodged bar chart doesn't tell us immediately the relative proportions. To do that, we need to turn to stacked bar chart and visualize the percentages. First, let's use the function `add_bar_label_pos()` to add to `dat_pct` the label positions so that we can label the stacked bars.
```{r}
# make a functions to be used for adding columns of 
# bar label positions to the input data frame
f = add_bar_label_pos(dat_pct)
# add bar label positions based on pct
dat_pct_w_pos = f("year_cat", "pct") 
print(dat_pct_w_pos)
```

We can now draw the stacked bar chart with labels in the middle of the bar bodies.
```{r, barplot_stacked_pct_midlab, fig.cap="Percent of Films that Made or Lost Money for Each Time Period"} 
plt = mk_barplot(dat_pct_w_pos)
title = "Percent of Films that Made/Lost Money for Each Time Period"
p = plt("year_cat", "pct", fillby="made_money", barpos="stack", 
        main=title, ylab = "Percent", barlab="pct", barlab_use_pct=T)
p = scale_axis(p, scale="pct")  
p = p + ggplot2::scale_fill_manual(values = c(purple, green))
p
```  

Now, it's your turn. Use `str(films)` to explore the variable types in the `films` data. Pick two categorical variables and one continuous variable. Try to visualize the relationships amongst them. See if you can dig out any hidden relationships. To do that, you may need to perform some data aggregation or slicing. Good luck and I'll see you in the next chapter, where we'll learn how to make Tufte bar chart. 