---
title: "02-04-Simple-Logit-Models"
author: "gmlang"
date: "April 3, 2015"
output: pdf_document
---

```{r setup}
library(knitr)
opts_chunk$set(comment = "", warning = FALSE, message = FALSE, tidy = FALSE,
               echo = TRUE, fig.width = 6, fig.height = 6, dev = 'png')
options(width = 100, scipen = 5, digits = 5)
```

## I'll use it to demo boxplots. 

First, let's draw boxplots of budget vs. years. 
```{r, warning=FALSE, message=FALSE}
# call the films dataset make a function that will draw boxplots 
# using the variables in the films data set
plt = mk_boxplot(films)

# plot distributions of budget over the years
title1 = "Annual Distribution of Budget from 1913 to 2014"
p = plt("year_cat", "budget", ylab="budget", main=title1)
print(p)
```

We see the y-axis tick labels are expressed in scientific notations. This makes it difficult to read. We can use the comma scale on the y-axis, which will display the numbers in 000,000 format.
```{r}
scale_axis(p, "y", scale = "comma")
```

We also observe that all the boxes are squashed down, indicating budget is heavily right-skewed. We can use either the log scale or the log10 scale on the y-axis. Once again, this can be easily done using the function `scale_axis()`.
```{r}
scale_axis(p, "y", scale = "log")
scale_axis(p, "y", scale = "log10")
scale_axis(p, "y", scale = "log2")
```
