```{r setup}
library(knitr)
opts_chunk$set(comment = "", warning = FALSE, message = FALSE, tidy = FALSE,
               echo = TRUE, fig.path='images/', fig.width = 6, fig.height = 6, 
               dev = 'png') # don't use fig.align, which forces html img code instead of md code
options(width = 100, scipen = 5, digits = 5)
```

## Histogram

As we've already seen from the last chapter, histogram, density plot and boxplot are for displaying the distribution of a continuous variable. We'll look at histogram in this section, and density plot and boxplot in the next two sections. Before we start, make sure you load the `ezplot` library first. And the ezplot function for making histogram is `mk_distplot()`.
```{r}
library(ezplot)
```


```{r}
# plot ratings distribution
plt = mk_distplot(dat)
title2 = "Distribution of Ratings (1913-2014)"
p = plt("rating", binw=0.3, xlab="rating", main=title2, add_vline_mean=T) 
p = ezplot::web_display(p)
print(p)

        # plot histogram to show the distribution of lengths
        plt = ezplot::mk_distplot(dat)
        title1 = "Distribution of Film Lengths"
        p = plt("length", xlab="minutes", main=title1, add_vline_mean=T)
        p = ezplot::scale_axis(p, "y", use_comma=T)
        p = ezplot::web_display(p)
        print(p)

```

## We'll plot dist first. The Q-Q plot shows that it isn't normally distributed. A normal variable would have all the blue dots form a line along the 45 degree line.  
```{r, target_vs_cat, fig.path='images/', fig.cap=""}
plt_dist(cars, "speed")
```

## We'll plot speed next. We see speed is more or less normally distributed.
```{r, warning=FALSE, message=FALSE}

```

The default color is color-blind friendly.

## I'll use it to demo boxplots. 

First, let's draw boxplots of budget vs. years. 
```{r, warning=FALSE, message=FALSE}
# call the films dataset make a function that will draw boxplots 
# using the variables in the films data set
plt = mk_boxplot(films)

# plot distributions of budget over the years
title1 = "Annual Distribution of Budget from 1913 to 2014"
p = plt("year_cat", "budget", ylab="budget", main=title1)
print(p)
```

We see the y-axis tick labels are expressed in scientific notations. This makes it difficult to read. We can use the comma scale on the y-axis, which will display the numbers in 000,000 format.
```{r}
scale_axis(p, "y", scale = "comma")
```

We also observe that all the boxes are squashed down, indicating budget is heavily right-skewed. We can use either the log scale or the log10 scale on the y-axis. Once again, this can be easily done using the function `scale_axis()`.
```{r}
scale_axis(p, "y", scale = "log")
scale_axis(p, "y", scale = "log10")
scale_axis(p, "y", scale = "log2")
```
