### Stacked Area Chart

Stacked area chart is something Economists use frequently. For example, if you leaf through the book [Capital in the Twenty-First Century](http://www.amazon.com/gp/product/067443000X/ref=as_li_tl?ie=UTF8&camp=1789&creative=9325&creativeASIN=067443000X&linkCode=as2&tag=cabaceo-20&linkId=VFX64EPFR3YKA7OG), you'll find many stacked area charts. A stacked area chart is the continuous analog of a stacked bar chart. We can use it to show how different components of the whole vary over time. It's important
to choose the order in which the different components are stacked because as you move up the stacks, it becomes increasingly difficult to see the patterns. I don't use stacked area chart that often, but if you ever need to use it, the `mk_areaplot()` function can save you a lot of time. Let's see it works. The ezplot package comes with a dataset of online advertising revenues between 2000 and 2014 broken down by 13 different revenue channels. We'll make a stacked area chart to show how revenue progressed from 2000 to 2014 for each channel.

First, let's look at the data and change it to long format.
```{r}
library(ezplot)
library(tidyr)
library(dplyr)
# original data
str(ads)
# wide format to long format
dat = ads %>% gather(type, rev, -year)
str(dat)
head(dat)
```      

Next, we can easily draw a stacked area chart using `mk_areaplot()`.
```{r, areaplot_amt, fig.cap="Online Ads Revenue 2000-2014"} 
plt = mk_areaplot(dat)
p = plt("year", "rev", fillby = "type", ylab = "Revenue (in Billions of USD)",
        main = "Internet Advertising Revenue")
# make x-axis look nice and use brewer colors instead of default
p + ggplot2::scale_x_continuous(limit = c(2000, 2014),
                                breaks = seq(2000, 2014, 2)) +
        ggplot2::scale_fill_brewer(palette = "Set3")
```

We can also visualize the revenue percentage of each channel over the years. First, we calculate the revenue percentage of each channel for each year.
```{r}
dat2 = dat %>% group_by(year) %>% mutate(total = sum(rev), pct = rev / total)
head(dat2)
```

Next, we run the same code, replacing "dat" with "dat2" and "rev" with "pct".
```{r, areaplot_pct, fig.cap="Online Ads Revenue Percent 2000-2014"} 
plt = mk_areaplot(dat2)
p = plt("year", "pct", fillby = "type", 
        main = "Percent of Overall Online Ads Revenue")
# change the y-axis to display percent instead of decimals
p = scale_axis(p, "y", scale = "pct")
p + ggplot2::scale_x_continuous(limit = c(2000, 2014), 
                                breaks = seq(2000, 2014, 2)) +
        ggplot2::scale_fill_brewer(palette = "Set3")
```

That's it. Now go have some fun making youself some stack area charts. When you come back for the next section, we'll talk about the line plot, which is for displaying timeseries data. 