## Likert Chart

A special kind of horizontal bar chart is the horizontal diverging bar chart, also called the likert chart. Let's see an example.

```{r, likert_mpaa_cnt, fig.cap="Frequencies of Profitable vs. Unprofitable Films for each MPAA rating"} 
library(ezplot)
library(dplyr)
df = films %>% # convert implicit NA to explicit "(Missing)"
        mutate(mpaa = forcats::fct_explicit_na(mpaa)) %>% 
        count(mpaa, made_money) %>% group_by(mpaa) %>%
        mutate(pct = n/sum(n)) %>% ungroup()
plt = mk_likertplot(df)
plt(xvar = "n", yvar = "mpaa", fillby = "made_money", 
    fillby_lvls = c("no", "yes"), yorder = "ascend")
```

We've already seen how to use `xvar`, `yvar`, `fillby`, and `yorder` before. The only parameter new here is `fillby_lvls`. We need to give it a character vector containing the unique levels of the `fillby` variable. The order of these values from left to right corresponds to the colored stacked bars from left to right. In this example, we set `fillby_lvls = c("no", "yes")`, as a result, the bars to the left of `x = 0` correspond to `made_money = no`, and to the right of `x = 0` correspond to `made_money = yes`. We can also show percent instead of raw count.

```{r, likert_mpaa_pct, fig.cap="Percents of Profitable vs. Unprofitable Films for each MPAA rating"} 
plt("pct", "mpaa", fillby = "made_money", fillby_lvls = c("no", "yes"), 
    legend_title = "Is profitable?", x_as_pct = TRUE)
```

Let's consider another example by first making some fake data.

```{r}
df = data.frame(item = rep(LETTERS[1:5], 4),
                slope = c(rep("North", 10), rep("South", 10)),
                type = rep(c(rep("native", 5), rep("introduced", 5)), 2),
                spp = as.integer(abs(rnorm(20, 5, 2)))
                ) %>% 
        mutate(spp = ifelse(type == "introduced", spp+1, spp),
               sppInv = ifelse(type == "native", spp, spp*-1))
head(df)
tail(df)
```

Let's focus on North and ignore South. 

```{r}
plt = mk_likertplot(df %>% filter(slope == "North"))
```

The variable `sppInv` is < 0 when `type` is "introduced", and > 0 when type is 
"native". We can make a likert chart to show the values of `sppInv` by `type` for
each `item`.

```{r, likert_north_sppInv, fig.cap="sppInv by type for each item"} 
plt("sppInv", "item", fillby = "type", 
    fillby_lvls = c("introduced", "native"),
    legend_pos = "top")
```

On the other hand, the variable `spp` is always > 0. Let's also make a likert 
chart to show the values of `spp` by `type` for each `item`.

```{r, likert_north_spp, fig.cap="spp by type for each item"} 
plt("spp", "item", fillby = "type", 
    fillby_lvls = c("introduced", "native"),
    legend_pos = "bottom")
```

To summarize, `mk_likertplot()` can work with both positive and negative x values
and show correct x-tick labels. When x-values are negative, the negative x-axis labels the ticks with negative numbers. When x-values are positive, the positive x-axis labels the ticks with positive numbers. 

Liker charts are commonly used for survey response data. For example, the dataset `ab3` contains respondents' confidence ratings for the future economy of 12 Arabic countries. Respondents were asked, "What do you think will be the economic situation in your country during the next few years (3-5 years) compared to the current situation?". We can visualize the info on a likert chart. 

```{r, likert_ab3, fig.cap="12 Arabic Countries Economic Outlook Survey Results"} 
df = ab3 %>% tidyr::gather(opinion, pct, -Country)
lvls = unique(df$opinion)
plt = mk_likertplot(df)
plt("pct", "Country", fillby = "opinion", fillby_lvls = lvls, 
    x_as_pct = TRUE, font_size = 9) %>%
    add_labs(xlab = NULL, 
             title = "Confidence for 12 arabic countries' economy")
```


Here's your homework:

1. Read the document of `mk_likertplot()`. You can pull it up by running 
`?mk_likertplot` in Rstudio. 
2. There's a R package called `likert` that is more comprehensive for analyzing
and visualizing Likert-type items. If you work with survey data a lot, you may
want to check it out. The package link is located at [https://github.com/jbryer/likert](https://github.com/jbryer/likert).
