## Horizontal Bar Chart & Lollipop Plot

We've discussed two ezplot functions: `mk_barplot_freq()` and 
`mk_barplot_resp()`. They allow us to easily make vertical bar charts. They have two counterparts: `mk_barploth_freq()` and `mk_barploth_resp()`, which can be used to make horizontal bar charts. Let's produce the horizontal versions of the bar charts we made previously.

The following examples show how to use `mk_barploth_freq()`.

```{r}
library(ezplot)
plt = mk_barploth_freq(films)
```

```{r, barploth_freq_mpaa_cnt, fig.cap="Frequency of MPAA", dpi=300, fig.width=7, fig.height=7} 
plt("mpaa", yorder = "descend", label_decimals = 2)
```      

```{r, barploth_freq_mpaa_pct, fig.cap="Relative Frequency of MPAA", dpi=300, fig.width=7, fig.height=7} 
plt("mpaa", show_pct = T, yorder = "descend") 
```

```{r, barploth_dodged, fig.cap="Number of Profitable vs. Unprofitable Films for Each Time Period", dpi=300, fig.width=7, fig.height=7} 
plt(yvar = "year_cat", fillby = "made_money", label_size = 0) 
```  

```{r, barploth_stacked, fig.cap="Percents of Profitable vs. Unprofitable Films for Each Time Period", dpi=300, fig.width=7, fig.height=7} 
plt(yvar = "year_cat", fillby = "made_money", show_pct = TRUE, 
    legend_title = "Is profitable?")
```  

The next examples show how to use `mk_barploth_resp()`.

```{r}
library(dplyr)
df = films %>% count(mpaa) %>% mutate(pct = n / sum(n))
plt = mk_barploth_resp(df)
```

```{r, barploth_resp_mpaa_cnt, fig.cap="Frequency of MPAA", dpi=300, fig.width=7, fig.height=7} 
plt(xvar = "n", yvar = "mpaa", label_decimals = 0) %>% 
        add_labs(xlab = "Frequency")
```  

```{r, barploth_resp_mpaa_pct, fig.cap="Relative Frequency of MPAA", dpi=300, fig.width=7, fig.height=7}   
plt(xvar = "pct", yvar = "mpaa", show_pct = TRUE, 
    label_decimals = 2, font_size = 9)
```

```{r, barploth_mpaa_vs_bo, fig.cap="Boxoffice by MPAA", dpi=300, fig.width=7, fig.height=7} 
plt = mk_barploth_resp(films)
plt("boxoffice", "mpaa", yorder = "descend", 
    font_size = 10, label_decimals = 0) %>% 
        rotate_axis_text(10)
```  

```{r, barploth_dodged_p3, fig.cap="Votes of Profitable and Unprofitable Films for each MAPP rating", dpi=300, fig.width=7, fig.height=7} 
plt("votes", "mpaa", fillby = "made_money", label_size = 0, 
    font_size = 9, legend_pos = "top") %>% 
        rotate_axis_text(15)
```

An alternative of horizontal bar chart is the lollipop chart. They are exchangeable. Let's make both charts with the following dataset.

```{r}
df = read.csv(text="category,pct
               Other,0.09
               South Asian/South Asian Americans,0.12
               Interngenerational/Generational,0.21
               S Asian/Asian Americans,0.25
               Muslim Observance,0.29
               Africa/Pan Africa/African Americans,0.34
               Gender Equity,0.34
               Disability Advocacy,0.49
               European/European Americans,0.52
               Veteran,0.54
               Pacific Islander/Pacific Islander Americans,0.59
               Non-Traditional Students,0.61
               Religious Equity,0.64
               Caribbean/Caribbean Americans,0.67
               Latino/Latina,0.69
               Middle Eastern Heritages and Traditions,0.73
               Trans-racial Adoptee/Parent,0.76
               LBGTQ/Ally,0.79
               Mixed Race,0.80
               Jewish Heritage/Observance,0.85
               International Students,0.87", 
              stringsAsFactors = FALSE, sep = ",", header = TRUE)
# change category to factor and order its levels in ascending order of pct 
df$category = reorder(df$category, df$pct)
```

```{r, barploth_vs_lollipop_p1, fig.cap="Horizontal Bar Chart Demo", dpi=300, fig.width=7, fig.height=7} 
plt = mk_barploth_resp(df)
plt("pct", "category", yorder = "descend", 
    font_size = 10, show_pct = TRUE, label_decimals = 0)
```

```{r, barploth_vs_lollipop_p2, fig.cap="Lollipop Chart Demo", dpi=300, fig.width=7, fig.height=7} 
plt = mk_lollipop(df)
plt("pct", "category", yorder = "descend", 
    font_size = 10, show_pct = TRUE, label_decimals = 0)
```
