## Regular Bar Chart

What if we're given a summary dataset where the frequencies are already tallied? How can we visualize the frequencies on a bar chart? For example, let's create a data frame with counts and percentages of the `mpaa` categories. 

```{r}
library(dplyr)
df = films %>% count(mpaa) %>% mutate(pct = n / sum(n))
df
```

How can we make a bar chart to visualize the `n` values? The answer lies in a different ezplot function, `mk_barplot_resp()`. 

```{r, barplot_resp_mpaa_cnt, fig.cap="Frequency of MPAA"} 
plt = mk_barplot_resp(df)
p = plt(xvar = "mpaa", yvar = "n", label_decimals = 0)
add_labs(p, ylab = "Frequency")
```  

Notice that in addition to supplying a categorical variable name to `xvar`, we also need to supply a continuous variable name to `yvar`. We created the above chart by setting `yvar = "n"`, and we now set `yvar = "pct"` to visualize the relative frequencies.

```{r, barplot_resp_mpaa_pct, fig.cap="Relative Frequency of MPAA"}   
plt(xvar = "mpaa", yvar = "pct", show_pct = TRUE, 
    label_decimals = 2, font_size = 9)
```

What will happen if you set `show_pct = FALSE`? Try it.

The function `mk_barplot_resp()` is actually more powerful than the example I just gave. Consider the following dataset, which further splits the counts of each MPAA category according to if the films made money or not.

```{r}
df2 = films %>% count(mpaa, made_money) %>% mutate(pct = n / sum(n))
df2
```

What will happen if we make a bar chart using `df2`? We'll get exactly the same bar chart as when using `df`! This is because `mk_barplot_resp()` is smart enough to aggregate the `n` values for the same `mpaa` category.

```{r, barplot_resp_mpaa_cnt_p2, fig.cap="Frequency of MPAA"} 
plt = mk_barplot_resp(df2)
p = plt(xvar = "mpaa", yvar = "n", label_decimals = 0) 
add_labs(p, ylab = "Frequency")
```

To summarise, `mk_barplot_resp()` aggregates the y values for each x category before making a bar chart. Now we know this, we can use it to plot the total boxoffice for each MPAA rating.

```{r, barplot_mpaa_vs_bo, fig.cap="Boxoffice by MPAA"} 
plt = mk_barplot_resp(films)
plt("mpaa", "boxoffice", xorder = "descend", 
    font_size = 10, label_decimals = 0)
```  

Now try the following exercises for homework.

1. Read the document of `mk_barplot_resp()`. You can pull up the documents by running `?mk_barplot_resp` in Rstudio. 
2. Make a bar chart to show the total budget of the films for each MPAA rating.
3. Make a bar chart to show the total boxoffice of profitable vs. unprofitable
films. 

