## Heatmap

Let's start with an example. Consider the dataset `nba`.
```{r}
library(dplyr)
library(tidyr)
library(ezplot)
# look at the first 5 rows and 8 columns
nba[1:5, 1:8]
# check the dimensions
dim(nba)
# check the colnames
colnames(nba)
```      

The variable `Name` contains players' names. It's a factor with levels ordered 
alphabetically. Let's reorder the levels in ascending order of the points the 
players scored.
```{r} 
str(nba$Name)
levels(nba$Name)
nba$Name = with(nba, reorder(Name, PTS))
```

The other variables are various performance statistics. In order to visualize 
the data in a heatmap, we first need to put the data in long format, a.k.a., we 
need to gather the names of the statistics in one column and their values in 
another column.
```{r} 
nba_m = nba %>% gather(stats, val, -Name)
head(nba_m)
```

Let's scale the values of every performance statistics so that they are between 
0 and 1. 
```{r}
dat = nba_m %>% group_by(stats) %>% mutate(val_scaled = scales::rescale(val))
head(dat)
```

With the data prep work done, we're ready to make a heatmap using the 
`mk_heatmap()` function.
```{r, heatmap_nba, fig.cap="NBA Performance Statistics"} 
plt = mk_heatmap(dat)
plt(xvar = "stats", yvar = "Name", fillby = "val_scaled") %>%
        rotate_axis_text(text_angle_x = 90, vjust_x = 0.5) %>% 
        add_labs(caption = "data source: flowingdata.com")
```

Notice we used `rotate_axis_text()` to rotate the x-tick text by 90 degrees and
vertically adjusted the text by 0.5. Run the command `?rotate_axis_text` to read
its document to learn more about how to use it. 

Not only `mk_heatmap()` allows us to make one heatmap quickly, it also enables
us to make multiple heatmaps in one plot with no sweat. Let's see another 
example. The dataset `attacks_by_country` has the number of internet 
attacks of ten countries for each hour of a day during a fixed time period. 
```{r}
str(attacks_by_country)
```

We can draw a heatmap for each country, showing the severity of attacks over 
time. Pay attention to the usage of `facet_by` and `facet_ncol` parameters in
the following code.
```{r, heatmap_attacks_by_country, fig.cap="Internet Attacks overtime by country"}
plt = mk_heatmap(attacks_by_country)
plt("hour", "wkday", fillby ="n", facet_by = "country", facet_ncol = 2) %>%
        add_labs(title = "Attacks per weekday & time of day by country")
```


Now it's your turn. Try the following exercises for homework.

1. Derive from `films` a data frame with 3 columns: `year_cat`, `made_money` and
`n`, where `n` counts the number of films. Hint: `?dplyr::count()`. Afterwards, 
make a heatmap to display the data.
2. Derive from `films` a data frame with 3 columns: `year_cat`, `action` and
`avg_rating`, where `avg_rating` summarizes the average rating. Hint: 
`?dplyr::group_by()` and `?dplyr::summarize()`. Afterwards, make a heatmap to
display the data.
3. Read the document of `mk_heatmap()` by running `?mk_heatmap` in Rstudio. 
What does the parameter `palette` do? Repeat exercise 1 and 2 using different 
values for `palette`.

